
\section{Overview}

The deep learning models have transformed the modern society by its superior
performance. The complexity of deep learning model is increased at an
unprecedented pace in many scientific and engineering domains. Meanwhile, deep
learning tools now leverage millions or billions of images/video/text/audio to
learn powerful nonlinear models. These models are capable of producing highly
accurate predictions, sometimes surpassing human accuracy. However, a
substantial gap remains between successful predictive models and concrete human
understandable scientific knowledge. Most deep predictive models are black boxes hard to understand even by machine learning experts, not to mention varied domain scientists who are not necessarily well-trained in machine learning. 

\paragraph{Objectives.}
The primal focus of this project is the research of novel deep saliency
maximization methods and their applications for text classification. Our goal is
to design novel functions for the saliency score with robust and better
performance, to design efficient optimization algorithms for saliency estimation
with faster convergence, and to broaden the impact of deep saliency maximization
in various medical applications.

\paragraph{Intellectual Merits.} We plan to address the aforementioned problems
from the following perspectives.
\begin{itemize}
\item \textbf{Novel Saliency Estimation Methods.} We propose .... The propose
  method...
\item \textbf{}
\item \textbf{}
\item \textbf{Broadening Applications in Natural Language Prediction Tasks.} 
\end{itemize}


\section{Model Explainablility and Problem Setups}

\subsection{Model Explainablility}

\subsection{Saliency Estimation}


\section{The proposed Research} Description of the proposed research in math.
\subsection{Drawbacks of X (previously used method)}
\subsection{Normalized Linear Gaussian Perturbation}
\paragraph{Problem Statement.}{Write One paragraph to introduce the background
\paragraph{Background.}
\paragraph{Proposed Research}  Aim 1. Aim 2.
\subsection{Machine-Understandable Saliency Estimation}
\paragraph{Problem Statement.}{Write One paragraph to introduce the background
Y\paragraph{Background.}
\paragraph{Proposed Research}  Aim 1. Aim 2.
\subsection{LASSO-Regularized and Machine-Understandable Saliency Estimation}
\paragraph{Problem Statement.}{Write One paragraph to introduce the background
\paragraph{Background.}
\paragraph{Proposed Research} Aim 1. Aim 2.  

\subsubsection{Machine-Understandable}
\subsubsection{LASSO-Regularized Estimation (Rename it)}
\subsubsection{Statistical consistency (Rename the title)}

\subsection{Applications in Natural Language Prediction}



\section{Data Infrastructure Development}
We will leverage significant resources already available at GWU on imaging
hardware and GPU computing hardware (see Facilities and Equipments \label{sec: }

\label{sec: }

\subparagraph{HL}



\section{Evaluation Plan}


\section{Intellectual Merits}



